Figures

### 2020-04-01 figures/08_exploratory_dotplot.Rmd
turn off clustering tree lines

pheatmap::pheatmap(
  t(dt_tp_hmap),
  # color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
  #                                          "Reds"))(100),
  cluster_cols = TRUE, cluster_rows = TRUE,
  na.col = "grey",
  cellheight = 8, cellwidth = 8, treeheight_col = 20, treeheight_row = 40)
```

>>>>

pheatmap::pheatmap(
  t(dt_tp_hmap),
  # color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
  #                                          "Reds"))(100),
  cluster_cols = TRUE, cluster_rows = TRUE,
  na.col = "grey",
  cellheight = 8, cellwidth = 8, treeheight_col = 0, treeheight_row = 0)
```
